A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-02 pilot-publication/outcome-tables.Rmd
Add functions to generate outcome tables and save them to disk

## overall

@@

tables[["ci.level.0.75"]][["overall"]]

@@

## pre.training

@@

tables[["ci.level.0.75"]][["pre.training"]]

@@

## post.training

@@

tables[["ci.level.0.75"]][["post.training"]]

@@

## absolute.difference

@@

tables[["ci.level.0.75"]][["absolute.difference"]]

@@

## relative.difference

@@

tables[["ci.level.0.75"]][["relative.difference"]]

@@

## Post training outcome Standard care vs. ATLS

@@

tables[["ci.level.0.75"]][["Post training outcome Standard care vs. ATLS"]]

@@

## Post training outcome Standard care vs. PTC

@@

tables[["ci.level.0.75"]][["Post training outcome Standard care vs. PTC"]]

@@

## Post training outcome ATLS vs. PTC

@@

tables[["ci.level.0.75"]][["Post training outcome ATLS vs. PTC"]]

@@

## Change from baseline Standard care vs. ATLS

@@

tables[["ci.level.0.75"]][["Change from baseline Standard care vs. ATLS"]]

@@

## Change from baseline Standard care vs. PTC

@@

tables[["ci.level.0.75"]][["Change from baseline Standard care vs. PTC"]]

@@

## Change from baseline ATLS vs. PTC

@@

tables[["ci.level.0.75"]][["Change from baseline ATLS vs. PTC"]]

@@

tables[["ci.level.0.85"]][["overall"]]

@@

tables[["ci.level.0.85"]][["pre.training"]]

@@

tables[["ci.level.0.85"]][["post.training"]]

@@

tables[["ci.level.0.85"]][["absolute.difference"]]

@@

tables[["ci.level.0.85"]][["relative.difference"]]

@@

tables[["ci.level.0.85"]][["Post training outcome Standard care vs. ATLS"]]

@@

tables[["ci.level.0.85"]][["Post training outcome Standard care vs. PTC"]]

@@

tables[["ci.level.0.85"]][["Post training outcome ATLS vs. PTC"]]

@@

tables[["ci.level.0.85"]][["Change from baseline Standard care vs. ATLS"]]

@@

tables[["ci.level.0.85"]][["Change from baseline Standard care vs. PTC"]]

@@

tables[["ci.level.0.85"]][["Change from baseline ATLS vs. PTC"]]

@@

tables[["ci.level.0.95"]][["overall"]]

@@

tables[["ci.level.0.95"]][["pre.training"]]

@@

tables[["ci.level.0.95"]][["post.training"]]

@@

tables[["ci.level.0.95"]][["absolute.difference"]]

@@

tables[["ci.level.0.95"]][["relative.difference"]]

@@

tables[["ci.level.0.95"]][["Post training outcome Standard care vs. ATLS"]]

@@

tables[["ci.level.0.95"]][["Post training outcome Standard care vs. PTC"]]

@@

tables[["ci.level.0.95"]][["Post training outcome ATLS vs. PTC"]]

@@

tables[["ci.level.0.95"]][["Change from baseline Standard care vs. ATLS"]]

@@

tables[["ci.level.0.95"]][["Change from baseline Standard care vs. PTC"]]

@@

tables[["ci.level.0.95"]][["Change from baseline ATLS vs. PTC"]]

>>>>

## Outcomes in all patients during the entire study period, by treatment arm

@@

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

@@

## Outcomes in all patients before training, by treatment arm

@@

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients before training, by treatment arm"]]

@@

## Outcomes in all patients after training, by treatment arm

@@

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients after training, by treatment arm"]]

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

outcome.results.tables[["ci.level.0.75"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

@@

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients before training, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients after training, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

@@

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients before training, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Outcomes in all patients after training, by treatment arm"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

@@

outcome.results.tables[["ci.level.0.95"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]
